How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in \textit{Emys marmorata} (Testudinoidea, Emydidae).

### 2014-12-04 doc/draft_turtle.tex
multinomial selection buy AUC. fixed figure.

The observed AUC values for all of the optimal models are very low, values near 0.5 indicate that a model is no better than completely random assigment TABLE OR FIGURE. This means that in very few cases are any of the proposed classification schemes are generally poor descriptors of the observed variation. It appears that the data set is overwhelmed by noise, making any accurate classifications difficult at best. This observation is cemented with the generalizations of the models to the testing data set.

>>>>

The observed AUC values for all of the optimal models are very low, values near 0.5 indicate that a model is no better than completely random assigment (Fig. \ref{fig:sel}) TABLE OR FIGURE. This means that in very few cases are any of the proposed classification schemes are generally poor descriptors of the observed variation. It appears that the data set is overwhelmed by noise, making any accurate classifications difficult at best. This observation is cemented with the generalizations of the models to the testing data set.
